Reproducible Validation and Replication Studies in Nanoscale Physics

### 2020-07-25 tex/results.tex
a bit more on repro

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.

>>>>

Our signature reproducibility practice is to organize and share in an archival-quality repository (providing a global identifier) all digital artifacts associated with the results in the paper. 
This includes input files, configuration files, post-processing scripts, files specifying the build process and containerization (e.g., Docker files), and even cloud computing machine definitions, if applicable \cite{mesnard-barba2019}.
We call these openly shared file sets \emph{reproducibility packages}, or repro-packs for short.
As in our previous papers, it is possible to reproduce all the figures in this paper using the repro-packs shared in the manuscript GitHub repository, and archived separately in Figshare and Zenodo.
[LIST, EXPLAIN, CITE ARCHIVES] 
\pygbe is openly developed and shared under the BSD3-clause license via its repository at \url{https://github.com/barbagroup/pygbe}.
